My Past Work

### 2025-01-28 interests.qmd
Update Responsive

<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/Slidecraft-Hi-Fi-Prototype-Flow?page-id=0%3A1&amp;node-id=1-31&amp;starting-point-node-id=1%3A31&amp;embed-host=share">

</iframe>

@@

<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" 
src="https://embed.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/ChatGPT-Dashboard-Hi-Fi-Desktop-View-Prototype-Link?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&embed-host=share" 
allowfullscreen>

</iframe>

@@

<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" 
src="https://embed.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&embed-host=share" 
allowfullscreen>

</iframe>

>>>>

<div style="position: relative; width: 100%; height: 450px;">
  <iframe style="position: absolute; top: 0; left: 0; width: 100%; height: 100%; border: 1px solid rgba(0, 0, 0, 0.1);" src="https://embed.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/Slidecraft-Hi-Fi-Prototype-Flow?page-id=0%3A1&amp;node-id=1-31&amp;starting-point-node-id=1%3A31&amp;embed-host=share" allowfullscreen>
  </iframe>
</div>

@@

<div style="position: relative; width: 100%; height: 450px;">
  <iframe style="position: absolute; top: 0; left: 0; width: 100%; height: 100%; border: 1px solid rgba(0, 0, 0, 0.1);" src="https://embed.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&amp;node-id=1-228&amp;starting-point-node-id=1%3A228&amp;embed-host=share" allowfullscreen>
  </iframe>
</div>

@@

<div style="position: relative; width: 100%; height: 450px;">
  <iframe style="position: absolute; top: 0; left: 0; width: 100%; height: 100%; border: 1px solid rgba(0, 0, 0, 0.1);" src="https://embed.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&amp;node-id=89-2546&amp;starting-point-node-id=89%3A2546&amp;embed-host=share" allowfullscreen>
  </iframe>
</div>
